%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%% \photo[circle,noedge,left]{./examples/profile}
\name{Lawrence P.}{Gouger}
\position{Lead Software Engineer}
\address{566 Irish Hill Rd., Shelburne, VT, 05482, USA}

\mobile{+1 (310) 989-5684}
\email{larry.gouger@gmail.com}
\homepage{www.bunimo.com}
\github{lgouger}
\linkedin{lgouger}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
\twitter{@lgouger}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Parkside Securities}
  {San Francisco, CA 94111}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Lead Full Stack Developer, Server-side(Clojure)}
% How the letter is opened
% \letteropening{Dear Mr./Ms./Dr. LastName,}
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Lawrence P. Gouger~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{Why I am Looking}
I found Parkside Securities's open positions with a search on Indeed
for Clojure and California.

I currently live near Burlinton, VT and I work for the Dealer.com (DDC)
organization within Cox Automotive.  It's a great place to work, but I
hope that I've enjoyed my last Vermont winter.  I moved here in May
2018 from Southern California and I miss California.  I started
working for Dealer.com in 2013.  DDC had a small engineering
presence in Manhattan Beach, and I was hired as one of two Engineering
Managers.  With only about 15 engineers, I was always in a position to
pitch in and contribute to coding, testing and support.  When the
Manhattan Beach office was closed in 2017 I was offered the chance to
stay on as a remote employee working from CA with a team based in
Burlington, VT.\@ After a year of remote work, I decided to give
Vermont a try in hopes on advancement and to work in person with my
team.  Advancement did come, I moved to VT as a Team member, a Senior
Engineer and I've now advanced to the role of a Scrum Team Tech Lead,
though still classified as a Senior Engineer.

So I'm seaching to grow and I'm searching to get back to California.
Admittedly San Francisco and Manhattan Beach share very little.
Hearing that Parkside Securities is in a domain I know, FinTech, and
that you're using technologies that I enjoy like Clojure, make the
potential for a move appealing.

I've chosen to apply for the ``Lead Full Stack Developer, Server-side
(Clojure)'' position, but if as you read my cover letter and resume
you think I might be a better fit in another role, I'm open to the
possibility.  Also, I should note, that I've received both of my
COVID-19 vaccination shots.  I look forward to offices reopening, but
I understand if working remotely is initially required.

\lettersection{FinTech Experience}
I'm not sure it comes across in my resume, but I bring a great deal of
knowledge and experience in the Financial/Brokerage world.  I grew up
with the industry while working for nealy 20 years as an engineer and
manager at ITG (Investment Technology Group).  Today ITG is part of
Virtu Financial, though this purchase took place after my time at ITG.

While at ITG, I worked on backend systems like the order routing
system, which was simply called the Glue.  I also contributed to the
development of a frontend trading workstation called QuantEX.\@ This
frontend was hosted on a Sun workstation and over the years used
technologies like Sun Windows and MOTIF (X Windows).

At ITG, I was most proud to be part of the birth of Algorithmic
Trading at ITG.\@ Initially we called them Strategy Servers, and I
wrote the first one developed at ITG, the VWAP Server.  It's goal was
to trade the shares it was given throughout the trading day in a
manner that would get as close as possible to the VWAP (Volume
Weighted Average Price) for the period of the day the orders were
active.  While I was part of this engineering team, we also developed
a server we called SPI (Server for Price Improvement) which was
intended to execute it shares quickly, sitting on the far side of the
quote and periodically adjusting it's price to be marketable when the
spread narrowed.  We also wrote a smart OTC router, a server for
volume participation, and several new generations of VWAP style
servers.

I'm also proud of my time leading the development of POSIT Now (US)
and TriACT Canada Marketplace (CA).  They were offshoots of ITG's
POSIT Automated Trading System.  POSIT is classified as a Dark Pool,
anonymously matching buyers and sellers at the public market's
midpoint price.  The idea being that it didn't publish quotes for the
orders it held, it only published trades as matches were performed
several times a day.  Typically trading desks and institutional
traders used POSIT to try to trade illiquid sequrities without the
risk of moving the market.  POSIT Now operated on the same principle
but looked for matches more frequently during the day.  Lists of
securities submitted together played an important role.  List based
constraints could be put in place to prevent an unwanted imbalance.
For example, one could limit how much buys could exceed sells and the
reverse as well.  These constraints were aimed at aiding portfolio
transitions.

\lettersection{Clojure Interest} I've been developing tools and single
page web apps in Clojure and Clojurescript for the past 6 years.  I
attended 2 Clojure Conjs, one in Philadelphia in 2015 and one in
Durham in 2018. In between those I atttended 2 Clojure West
conferences in Seattle in 2016 and Portland in 2017.  At these conjs I
also attended the training that preceeded each conference, Clojure
training in Philadelphia, clojure.spec in Portland, and a Day of
Datomic in Durham.

I haven't been able to use Clojure in any of the systems officially
deployed while at Cox Automotive, but I have developed tools and
single page web apps to help with the running of our systems.  One
example is zkget, a command line tool to browse and search ZooKeeper.
Another was a SPA called adv-assist, to assist in working with
Facebook pages and our Advertising acounts.

Most recently I've been playing with Cognitect's AWS library.  Writing
tools to monitor Lambda functions, S3 buckets, and SQS queues.

To summarize my proficiencey in Clojure, I'm capable of solving
problems in Clojure, but I've always worked on Clojure projects on my
own.  I look forward to working with others to see how they solve
problems and share the techniques I've used.  In specific areas like
core.async or datomic, I've dabbled, but I haven't done anything
meaty. 

\lettersection{Tech Experience}
My current team is focused on OEM incentives applied to vehicles sold
by our Automotive dealership customers.  We are in a transition from
on-prem Java Spring apps hosted by Tomcat to Containerized deployments
using the AWS Elastice Container Service (ECS).  As the Scrum team's
Tech Lead, I'm investigating EKS (AWS hosted K8s), GitOps using tools
like ArgoCD, and Github Actions to build the Docker images to be
deployed.

The team has also been building serverless apps as well, AWS Lambdas and Step Functions.

\lettersection{In Closing}

Thank you for your consideration.  I hope to have the opportunity to
tell you more about who I am and what I can bring to Parkside
Securities.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
