%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Current Work Experience - Cox Automotive, Inc.}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvparagraph}
I was hired by Cox Automotive, then called Dealer.com, as an
Engineering Manager, one of two in their Manhattan Beach, CA office.
I managed engineers who were part of 2 scrum teams, a total of 7
individuals.
\end{cvparagraph}

\vspace{-1.00mm}

\begin{cvparagraph}
Prior to becoming an Engineering Manager in my career, I had been a
senior software engineer, and as an Engineering Manager, I kept my
hands in the code, usually by intercepting one-off requests that
risked derailing my team's planned efforts.\@ In late 2016, Cox
Automotive decided to end it's engineering presence in the Manhattan
Beach office.\@ After helping to wind down the engineering effort in
the office, I transitioned to an individual contributor role as a
Senior Developer.\@ In 2017 the entire Manhattan Beach office was
closed, and I began working remotely as a member of a Scrum team based
in Burlington, VT.\@ Being a California based developer working with a
team based in Burlington VT was difficult.\@ After working remotely for
a year I decided to relocate to Burlington, VT and work with my team
in person.\@ Moving to Burlington had two benefits, the direct, in
person interaction was more fun and it led to more advancement
opportunities.
\end{cvparagraph}


\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer{\enskip\cdotp\enskip}Scrum Tech Lead} % Job title
    {Dealer.com --- Platform Engineering} % Organization
    {Burlington, VT} % Location
    {July 2020 --- Present} % Date(s)
    {}
\end{cventries}

\vspace{-4.00mm}
\begin{cvparagraph}
Joined new Scrum team to pursue Scrum Team Tech Lead role. Dealer.com's Platform Engineering team is responsible for several backend systems supporting Dealer.com's Websites, Advertising and Inventory systems.
\end{cvparagraph}

\vspace{-2.00mm}
\begin{cventries}
\cventry
    {New Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {    
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{AWS:} ECS/Fargate, EKS}
        \item {\textbf{Containers:} Docker, Kubernetes}
        \item {\textbf{Infrastructure as Code (IaC):} Terragrunt \& Terraform}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Dealer.com --- Agency Advertising} % Organization
    {Burlington, VT \linebreak Manhattan Beach, CA} % Location
    {May 2017 --- July 2020} % Date(s)
    {}
\end{cventries}

\vspace{-4.00mm}
\begin{cvparagraph}
Joined team as an individual contributor following the closing of the
Dealer.com office in Manhattan Beach, CA.\@ For the first year I worked
remotely from CA for a VT based team.\@ In June 2018, I moved to VT
seeking to improve advancement opportunities.
\end{cvparagraph}

\vspace{-1.00mm}

\begin{cvparagraph}
The team's focus was on systems to support digital advertising at Google, Microsoft, Facebook, and Youtube.\@
Our systems enabled advertising the inventory of our dealership clients as their inventory changed.\@
I was responsible for the design, implementation, testing, deployment, and support of these systems.
\end{cvparagraph}

\vspace{-2.00mm}
\begin{cventries}

\cventry
    {New Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {    
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{AWS:} Lambda, API Gateway, SQS, SNS, RDS, DynamoDB, IAM, SSM, Secrets Manager, EC2, Elastic Beanstalk, Networking (vpc, subnets, security groups)}
        \item {\textbf{IaC:} Terraform \& Serverless}
        \item {\textbf{Python:} async programming using libraries: trio \& asks}
        \item {\textbf{Kotlin}}
      \end{cvitems}
    }

\pagebreak

%---------------------------------------------------------
  \cventry
    {Engineering Manager} % Job title
    {Dealer.com --- Social Applications Development} % Organization
    {Manhattan Beach, CA} % Location
    {Jan. 2013 --- May 2017} % Date(s)
    {}
    \vspace{-4.00mm}

  \cventry
    {Management Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    { \vspace{-0.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team Building, Sustainable development pace and Work/Life balance}
        \item {Regular 1-on-1 meetings and Quarterly checkins/reviews}
        \item {Hiring and Termination}
      \end{cvitems}
    }

  \cventry
    {Agile Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    { \vspace{-0.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scrum, Kanban}
        \item {SAFe 3.0 (A Cox variant of SAFe called CAFe)}
      \end{cvitems}
    }

  \cventry
    {Technical Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    { \vspace{-0.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Languages:} Java, Perl, Groovy}
        \item {\textbf{Spring:} Spring Boot, Spring Data, Spring AMQP, Spring Core Framework}
        \item {\textbf{Tools:} IntelliJ IDEA, maven, git, Grails}
      \end{cvitems}
    }

\end{cventries}

%---------------------------------------------------------
%---------------------------------------------------------

\cvsection{Previous Experience - ITG, Inc.}

\cvsubsection{Skills at ITG}

\begin{cventries}
  \cventry
    {Management Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Lead technological transitions (eg. from \CC{} on Solaris to \CS{} on Win32), Launched a remote team in NYC.}
      \item {Team Building, Team member reviews and one-on-ones, Hiring, Performance Improvement Plans, and Firing}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Development Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
    \begin{cvitems}
      \item {\textbf{Platforms:} Linux, Solaris, unix, JVM, Win32, CLR}
      \item {\textbf{Agile Skills:} Scrum, Extreme Programming, Pair Programming}
      \item {\textbf{Development Languages:} Java, C, \CC{} (gcc), \CS{}, Perl}
      \item {\textbf{Development Tools:} SVN, Clearcase, Eclipse, Visual Studio, Rally}
    \end{cvitems}  
    }
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Summary of Responsibilities}

\begin{cventries}

\cventry
    {Senior Engineering Manger} % Job title
    {ITG Platform Tools} % Organization
    {Culver City, CA} % Location
    {Oct. 2009 --- July 2011} % Date(s)
    {I managed a team developing tools to monitor trading within the firm.}

  \cventry
    {Engineering Manger} % Job title
    {POSIT Now \& Match NOW} % Organization
    {Culver City, CA} % Location
    {Sept. 2004 --- Oct. 2009} % Date(s)
    {POSIT Now and MATCHNow in Canada were ATSs (Automated Trading Systems)
for trading equities.\@ Orders submitted to these systems were
anonymous to minimize potential market impact, and trades executed by
the systems were at the midpoint of the national best bid and offer.}

  \cventry
    {Engineering Manger \& Senior Software Engineer} % Job title
    {Algorithmic Trading Systems} % Organization
    {Culver City, CA} % Location
    {May 1997 --- Sept. 2004} % Date(s)
    {I started as the developer of the first Algorithmic Trading System at
ITG, a VWAP Server.\@ It used the "Auto-Trading" capability of ITG's
QuantEX equity trading system.\@ I went on to lead the development of
four generations of very successful Algorithmic Trading systems at
ITG.}

  \cventry
    {Senior Software Engineering} % Job title
    {QuantEX \& Canadian QuantEX.} % Organization
    {Culver City, CA} % Location
    {Oct. 1991 --- May 1997} % Date(s)
    {ITG's QuantEX was an Equity Trading and Analytics application on a Sun
workstation.\@ While a member of the team I had the following roles,
Senior Developer, Tech Lead, and Manager.\@ My first engineering
management role was as the leader of the Canadian QuantEX development
team.}

\end{cventries}

%---------------------------------------------------------
%---------------------------------------------------------

\cvsection{Previous Experience --- TRW, Inc.}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Member of Technical Staff} % Job title
    {TRW Inc.} % Organization
    {Redondo Beach, CA} % Location
    {June 1985 --- Oct. 1991} % Date(s)
    {Senior Developer, C, SunOS/Solaris, worked on applications that exploited a TRW search technology called the Fast Data Finder.}

%---------------------------------------------------------
\end{cventries}


