%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Current Work Experience --- Cox Automotive, Inc.}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvparagraph}
I was hired by Cox Automotive, then called Dealer.com, as an
Engineering Manager, one of two in their Manhattan Beach, CA office.
I managed engineers who were parts of 2 scrum teams, a total of 7
individuals.
\end{cvparagraph}

%\vspace{-1.00mm}

\begin{cvparagraph}
Prior to becoming an Engineering Manager in my career, I had been a
software engineer, and after becoming an Engineering Manager, I kept my
hands in the code, usually by intercepting one-off requests that
risked derailing my teams' planned efforts.\@ In late 2016, Cox
Automotive decided to end its engineering presence in Manhattan
Beach.\@ At that point, I transitioned to an individual contributor role as a
Senior Developer, and I began working remotely as part of a Scrum team based
in Burlington, VT.\@ After working remotely for a year I chose to
relocate to Burlington, VT hoping to improve advancement opportunities.
\end{cvparagraph}


\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Lead Software Engineer{\enskip\cdotp\enskip}Scrum Tech Lead} % Job title
    {Cox Automotive. --- Automotive Client Insights / Command Center} % Organization
    {Burlington, VT} % Location
    {Aug 2024 --- Present} % Date(s)
    {}
\end{cventries}
% \vspace{-6.00mm}

\begin{cvparagraph}
I joined this newly forming scrum team focused on a new reporting tool, Command Center.
Its goal is to bring together Reporting and Analytics for a broad array of Cox products.
Currently each product sold by Cox Automotive includes its own data analytics and reporting systems.
Initially Command Center will be a jumping off point to the scattered reporting sub-systems, and slowly
take over reporting directly from within Command Center for more and more use cases.
\end{cvparagraph}

% \vspace{-2.00mm}
\begin{cventries}
\cventry{Accomplishments} % job title
    {} % organization
    {} % location
    {} % date(s)
    {%
      \begin{cvitems} % description(s) of tasks/responsibilities
      \item {Architected unified reporting platform consolidating data from 6 product lines}
      \item {Led technical design sessions and drove adoption of GitOps practices with Argo CD}
      \item {Designed scalable data pipeline using Snowflake/dbtCloud triggered by data publication events}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer{\enskip\cdotp\enskip}Scrum Tech Lead} % Job title
    {Cox Automotive. --- Dealer.com / Vehicle Incentives Processing} % Organization
    {Burlington, VT} % Location
    {Feb 2021 --- Aug 2024} % Date(s)
    {}
\end{cventries}
% \vspace{-6.00mm}

\begin{cvparagraph}
I joined the scrum team focused on Vehicle Incentives to bring it stability and leadership.
Dealer.com's (DDC) incentives team collects Cash, APR, and Lease incentives from multiple sources,
links them with the vehicles currently in inventory at our clients' dealerships,
and makes them available for display on the dealerships' DDC websites.
\end{cvparagraph}

% \vspace{-2.00mm}
\begin{cventries}
\cventry{Accomplishments} % job title
    {} % organization
    {} % location
    {} % date(s)
    {%
      \begin{cvitems} % description(s) of tasks/responsibilities
      \item {Processed tens of thousands of inventory updates impacted by active incentives}
      \item {Integrated with dozens of Incentive Providers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer{\enskip\cdotp\enskip}Scrum Tech Lead} % Job title
    {Cox Automotive --- Dealer.com / Platform Engineering} % Organization
    {Burlington, VT} % Location
    {July 2020 --- Feb 2021} % Date(s)
    {}
\end{cventries}
% \vspace{-6.00mm}

\begin{cvparagraph}
I joined the DDC Platform Scrum team to pursue a Scrum Team Tech Lead role. Dealer.com's Platform Engineering team is responsible for several backend systems supporting Dealer.com's Web sites, Advertising and Inventory systems. (Team Chemistry)
\end{cvparagraph}

% \vspace{-2.00mm}
\begin{cventries}
\cventry{Summary of Skills during this period} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{AWS Technologies:} ECS/Fargate, EKS, Elastic Beanstalk}
        \item {\textbf{Container Technologies:} Docker, Kubernetes}
        \item {\textbf{Infrastructure as Code (IaC):} Terragrunt \& Terraform}
        \item {\textbf{Spring Frameworks:} Core, Spring Cloud, Spring Webflux}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry{Senior Software Engineer} % Job title
    {Cox Automotive --- Dealer.com / Agency Advertising Engineering} % Organization
    {Burlington, VT{\vspace{1mm}\newline}Manhattan Beach, CA} % Location
    {May 2017 --- July 2020} % Date(s)
    {}
\end{cventries}
% \vspace{-6.00mm}

\begin{cvparagraph}
The team's focus was on systems to support digital advertising at Google, Microsoft, Facebook, and YouTube.\@
Our systems enabled advertising the inventory of our clients' dealerships as their inventory changed.\@
I was responsible for the design, implementation, testing, deployment, and support of these systems.
\end{cvparagraph}

% \vspace{-2.00mm}
\begin{cventries}

\cventry{Summary of Skills during this period} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{AWS:} Lambda, API Gateway, S3, SQS, SNS, RDS, DynamoDB, IAM, SSM, Secrets Manager, EC2, Elastic Beanstalk, Networking (vpc, subnets, security groups)}
        \item {\textbf{Infrastructure as Code (IaC):} Terraform \& Serverless}
        \item {\textbf{Development Languages:} Java, Python, and Groovy}
        \item {\textbf{Development Tools:} IntelliJ IDEA, maven, git, gradle, Jib}
        \item {\textbf{Spring Frameworks:} Spring Boot, Spring Data, Sprint RESTController, Spring Core Framework}
        \item {\textbf{Python Technologies:} async programming using libraries: trio \& asks, pipenv, poetry}
        \item {\textbf{Database Technologies:} MySQL (onprem, RDS, and Aurora), DynamoDB}
        \item {\textbf{API Technologies:} REST, Swagger/OpenAPI, gRPC, Spring Remoting}
        \item {\textbf{Messaging Technologies:} SQS, AmazonMQ, RabbitMQ}
        \item {\textbf{Other Technologies:} New Relic (APM, Infrastructure, Synthetics), LaunchDarkly}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry{Engineering Manager} % Job title
    {Cox Automotive --- Dealer.com / Social Applications Development} % Organization
    {Manhattan Beach, CA} % Location
    {Jan. 2013 --- May 2017} % Date(s)
    {}
    % \vspace{-6.00mm}

  \cventry{Leadership Skills} % Job title
    {} % Organizatio\textbf{api technologies:} rest, swagger/openapi, spring remoting}n
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Team Building:} Regular 1-on-1 meetings and Quarterly check-ins/reviews}
        \item {\textbf{Agile:} Scrum, Kanban}
      \end{cvitems}
    }

  \cventry{Technical Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Languages:} Java, Perl, Groovy}
        \item {\textbf{Spring:} Spring Boot, Spring Data, Spring AMQP, Spring Core Framework}
        \item {\textbf{Tools:} IntelliJ IDEA, maven, gradle, git, Grails}
        \item {\textbf{Database Technologies:} MySQL, MongoDB}
        \item {\textbf{API Technologies:} REST, Spring Remoting}
      \end{cvitems}
    }

\end{cventries}

%---------------------------------------------------------
%---------------------------------------------------------

\cvsection{Previous Experience --- ITG, Inc.}

%\cvsubsection{Skills at ITG}
\vspace{-1.00mm}

\begin{cventries}
  \cventry{Senior Engineering Manger} % Job title
    {ITG, Inc.} % Organization
    {Culver City, CA} % Location
    {Oct. 1991 --- July 2011} % Date(s)
    {}
  % \vspace{-6.00mm}

  \cventry{Leadership Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led technology transitions (eg.\ from \CC{} on Solaris to \CS{} on Win32), and launched a remote team in NYC.}
      \item {Team Building, Team member reviews and one-on-ones, Hiring, Performance Improvement Plans, and Firing}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry{Technical Skills} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {\vspace{-0.5mm}
    \begin{cvitems}
      \item {\textbf{Platforms:} Linux, Solaris, unix, JVM, Win32, CLR}
      \item {\textbf{Agile Skills:} Scrum, Extreme Programming, Pair Programming}
      \item {\textbf{Development Languages:} Java, C, \CC{} (gcc), \CS{}, Perl}
      \item {\textbf{Development Tools:} SVN, Clearcase, Eclipse, Visual Studio, Rally}
      \item {\textbf{Technologies:} Sybase ASE \& Aleri, IBM CPlex Optimizer}
    \end{cvitems}
    }
\end{cventries}

%---------------------------------------------------------
%\cvsubsection{Summary of Responsibilities}
%\vspace{-1.00mm}

\begin{cvsubentries}
  \cvsubentry{}{Senior Engineering Manger --- ITG Platform Tools}{Oct. 2009 --- July 2011}{}
  \cvsubentry{}{Engineering Manger --- POSIT Now \& Match NOW}{Sept. 2004 --- Oct. 2009}{}
  \cvsubentry{}{Engineering Manger \& Senior Software Engineer --- Algorithmic Trading Systems}{May 1997 --- Sept. 2004}{}
  \cvsubentry{}{Senior Software Engineer --- QuantEX \& Canadian QuantEX}{Oct. 1991 --- May 1997}{}
\end{cvsubentries}

%---------------------------------------------------------
%---------------------------------------------------------

\cvsection{Previous Experience --- TRW, Inc.}

\begin{cventries}

%---------------------------------------------------------
  \cventry{Senior Member of Technical Staff} % Job title
    {TRW Inc.} % Organization
    {Redondo Beach, CA} % Location
    {June 1985 --- Oct. 1991} % Date(s)
    {Senior Developer, C, SunOS/Solaris, worked on applications that exploited a TRW search technology called the Fast Data Finder.}

%---------------------------------------------------------
\end{cventries}


